Visualizations for article

### 2015-12-02 101-visualizations-for-article.Rmd
Midway point in big graph of section borrowings

---
title: "Visualizations for article"
author: "Lincoln Mullen"
date: "November 3, 2015"
output: html_document
---

@@

```{r}
minimum_n <- 50
top_matches <- 4
codes_not_to_plot <- c(
  "CO868", 
#   "CT1879", 
  "FL1847", 
  "FL1892", 
  "GA1851",
  "GA1860", 
#   "HI1859", 
#   "HI1897", 
  "IL1866", 
#   "LA1825", 
#   "LA1844", 
#   "MS1848", 
#   "MS1857", 
  "NY1876", 
  "NY1879",
  "VA1860", 
#   "VA1893", 
  "WV1868" 
  )
# codes_not_to_plot <- NULL

@@

edge_size_clamp <- function(g, multiplier = 20, max_val = 6, min_val = 0.5) {
  w <- E(g)$weight * multiplier
  w[w > max_val] <- max_val
  w[w < min_val] <- min_val
  w
}

>>>>

---
title: "Visualizations for article"
author: "Lincoln Mullen"
date: "November 3, 2015"
---

@@

```{r}
minimum_n <- 20
top_matches <- 3
codes_not_to_plot <- c(
  # "CO868", 
#   "CT1879", 
  # "FL1847", 
  # "FL1892", 
  "GA1851",
  "GA1860", 
  "HI1859", 
  "HI1897", 
  # "IL1866", 
  "LA1825", 
  "LA1844", 
#   "MS1848", 
#   "MS1857", 
  # "NY1876", 
  # "NY1879",
  # "VA1860", 
  "VA1893", 
  "WV1868" 
  )
# codes_not_to_plot <- NULL

@@

edge_size_clamp <- function(g, multiplier = 20, max_val = 6, min_val = 1) {
  w <- E(g)$weight * multiplier
  w[w > max_val] <- max_val
  w[w < min_val] <- min_val
  w
}
